Model_CFU

### 2017-01-05 code/HumanCdGF_cdiff_colonization.Rmd
Add plot predicting CFU without High and Low

>>>>

#### Remove High and Low CFU sources

```{r all without 581 or 1134/1146}
cfu_wo_hilo_df <- colonized_cfu %>% 
    select(mouse_id, human_source, log_cfu_med) %>% 
    right_join(community_all_d0) %>% 
    filter(!human_source %in% c('DA00581', 'DA01134','DA01146')) %>% 
    select(-mouse_id) %>% 
    filter(!is.na(log_cfu_med))
cfu_wo_hilo_df$human_source <- factor(cfu_wo_hilo_df$human_source)

set.seed(seed)
cfu_wo_hilo_rf <- randomForest(cfu_wo_hilo_df[ , -2], cfu_wo_hilo_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
top_features_wo_hilo <- head(sort(importance(cfu_wo_hilo_rf)[,1],decreasing = T), n_features)

data.frame(Observed = cfu_wo_hilo_df$log_cfu_med, 
           Predicted = cfu_wo_hilo_rf$predicted) %>% 
  ggplot(aes(x = Predicted, y = Observed)) + geom_point() +
    xlim(5,9) + ylim(5,9) + 
    annotate('text', label = paste0(round(tail(cfu_wo_hilo_rf$rsq, 1), 4)*100, '% Var Explained'),
             x = 5.5, y = 8.9) + 
    theme(panel.background = element_rect(linetype = 1, size = 1, fill = 'white', color = 'black'),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank()) +
  labs(x = 'Predicted Colonization (log CFU)', y = 'Observed Colonization (log CFU)')
```
